%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {Equal Experts (Embedded at Travelopia)} % Organization
    {Bengaluru, India} % Location
    {September 22' - Present} % Date(s)
    {
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Leading the Apps Squad across Yachts (The Moorings \& Sunsail) and Le Boat brands - front-end engineering, checkout modernization, payment systems, and AI-powered internal tooling.}
			\item {Reverse-engineered an entire legacy application in 6 days using AI-assisted workflows (Claude Code \& Cursor) - originally scoped at 4 months.}
			\item {Led Credit Card Surcharge for Yachts Checkout using PaymentJS with Fiserv - estimated to save 5-7M GBP annually. First brand within Travelopia live for both online and phone bookings simultaneously.}
			\item {Replaced legacy Drupal Checkout with a modern SPA for The Moorings and Sunsail, rolled out to all regions and currencies. CTO and Brand Technology Partner present for go-live.}
			\item {Delivered Le Boat New Online Checkout as a full SPA redesign across 8 international websites in \textasciitilde{}6 weeks.}
			\item {Launched Le Boat Manage My Booking - crew management, extras selection, and instalment payments, built with AI-assisted delivery throughout.}
			\item {Built Le Boat Price Framing / Bundles (A/B tested, full rollout Dec 9). Ancillaries contribute 26\% of Le Boat's overall business - Phase 1 showed strong mobile conversion uplift.}
			\item {Building Voice IQ: AI-powered call coaching dashboard using Talkdesk + Gemini - transcription, LLM scoring, and coaching feedback for Sales/Support teams.}
		\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {InVideo} % Organization
    {Remote} % Location
    {November 21' - September 22'} % Date(s)
    {
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Architected and executed a large-scale code migration from Angular to React using Module Federation - improving build performance, team autonomy, and long-term maintainability.}
			\item {Made critical UI architectural decisions impacting the front-end of a product used by millions of creators worldwide.}
			\item {Provided on-call support and directly engaged with users to triage and resolve production issues, ensuring high availability for a real-time editing experience.}
		\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Consultant (Contract)} % Job title
    {ThoughtWorks} % Organization
    {Remote} % Location
    {August 20' - November 21'} % Date(s)
    {
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {IDFC First Bank: Built complete user journeys for iOS, Android, and Web using React Native with industry-first cloud-based hyper-personalization and server-side toggle-based journey enabling.}
			\item {Caterpillar: Developed features for a dealer/customer-facing PWA with deep Google Maps integration - asset tracking, geo-fencing, utilization optimization, and fleet-wide financial management.}
			\item {Metro Digital: Built a performance-focused portfolio website from scratch using Gatsby. Achieved 95+ Lighthouse scores across all categories.}
		\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {CoffeeBeans Consulting} % Organization
    {Bengaluru, India} % Location
    {January 20' - November 21'} % Date(s)
    {
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Talent500: Built features for Canvas, a next-gen ATS enabling multi-channel sourcing from proprietary talent pools to third-party job boards and LinkedIn.}
			\item {Unibiz: Conducted deep performance analysis of a heavy React application - identified memory leaks, raised issues with third-party library teams, and demonstrated measurable improvements.}
			\item {Organized the Food Code Sleep Hackathon, mentored new engineers, and led upskilling sessions on production-readiness.}
		\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer → Senior Engineer} % Job title
    {QBurst Technologies Pvt Ltd.} % Organization
    {Calicut, India} % Location
    {June 16' - January 20'} % Date(s)
    {
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Delivered 7+ client projects across SPA development (Angular, Vue, React), test automation (Selenium/Java), IoT data pipelines (Scala/Spark/Kafka), and D3.js data visualizations.}
			\item {Rocket Partners: Developed mobile + kiosk PWA applications for a retail supermarket chain. Code quality commended by client top management.}
			\item {Won special mention in "Game of Code" internal hackathon. Completed GCP Architecture and TensorFlow specializations.}
		\end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
